### 2025-01-26 analysis/analysis.qmd
fix(summaries): update model_class_id to reflect best performing model class

# yang2021an needs to be encoded for classification (currently just regression)
C_summary <- read.csv("C_summary.csv")
C_classes <- read.csv("C_study_class_n.csv")

@@

```
#### By class n = 2 vs. > 2
```{r}
C_summary$classes <- 0
C_summary[C_summary$n_classes < 3,]$classes <- "2"
C_summary[C_summary$n_classes >= 3,]$classes <- ">2"

@@

@@

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

>>>>

# yang2021an needs to be encoded for classification (currently just regression)
C_summary <- read.csv("C_summary.csv")

C_classes <- read.csv("C_study_class_n.csv")

@@

```
#### By class n = 2 vs. > 2
```{r}
C_summary$classes <- 0
C_summary[C_summary$n_classes == 2,]$classes <- "Binary"
C_summary[C_summary$n_classes >= 3,]$classes <- "Multiclass"

@@

```
```{r}
m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n, # could also change to n_classes
                 studlab = studyREF, # unique_id
                 data = C_summary,
                 subgroup = model_class_id,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

m.cor
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "N"),studlab = citekey)

```{r}
#| fig-width: 12
#| fig-height: 6
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "N"),studlab = studyREF)

gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))

@@

O

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
#       subgroup = model_class_id, 
#       subgroup = journal_type, 
       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

### 2025-01-26 analysis/preprocessing.qmd
fix(summaries): update model_class_id to reflect best performing model class

R_studies$feature_n_categories <-cut(R_studies$feature_n,
                                      breaks = c(0,18,260,
                                                 10000),
                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))

@@

# a combination of the two
R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
                                      breaks = c(0,15,501,653,20000),
                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
#table(R_studies$feature_n_complexity_genre)
```

@@

R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))

@@

R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 10000),
                                      labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))

R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,30,300,10000),
                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))

@@

# a combination of the two
R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
                                      breaks = c(0,15,501,653,10000),
                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
#table(R_studies$feature_n_complexity_genre)
```

@@

```{r}
C_summary <- summarise(group_by(C_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                        #feature_n_complexity_genre=first(feature_n_complexity_genre)
                        )
# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean

@@

>>>>

R_studies$feature_n_categories <-cut(R_studies$feature_n,
                                      breaks = c(0,18,260,
                                                 14460),
                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))

@@

# a combination of the two
R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
                                      breaks = c(0,15,501,653,14460),
                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
#table(R_studies$feature_n_complexity_genre)
```

@@

R_summary <- summarise(group_by(R_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))

### Now filter out best model
R_summary |> 
  ungroup() |> 
  filter(
    valuesMax == max(valuesMax), 
    .by = c(citekey, dimension)
  ) -> R_summary

@@

R_summary_split <- pivot_wider(R_summary,id_cols = c(citekey, model_class_id), names_from = c(dimension), values_from = valuesMax)

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 14460),
                                      labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))

R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,30,300,14460),
                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))

@@

# a combination of the two
R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
                                      breaks = c(0,15,501,653,14460),
                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
#table(R_studies$feature_n_complexity_genre)
```

@@

```{r}
C_summary <- summarise(group_by(C_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                        #feature_n_complexity_genre=first(feature_n_complexity_genre)
                        )
# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean

@@

C_summary |> 
  ungroup() |> 
  filter(
    valuesMax == max(valuesMax), 
    .by = c(citekey, dimension)
) -> C_summary
